What Does Reproducible Research Mean for Plant Pathology?

### 2017-04-23 README.rmd
Finalise conversion to R package
Ready for articles to be evaluated by us

Need to add bib entries to bib file in `inst/paper`

_Other changes_

- Add coverage
- Check spelling
- Finalise fetching references
- Add “examined_articles.bib” to `inst/paper`
- New function to get bib entries given a doi, `doi2bib()`
- Clean up vignettes
- Clean up README
- Use Travis and Appveyor
- Update packrat repository

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
[![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published

@@

Adam H Sparks (adamhsparks@gmail.com)
Emerson M Del Ponte
Zachary Foster
Niklas J Grünwald

@@

This repository is our research compendium that details our methodology for examining the state of reproducible research in plant pathology. The compendium contains all data, code, and text associated with the publication XXXX published in XXX. The `Rmd` files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted. Instructions on how to rerun the analysis to reproduce the results are found in the vingette, in the `vingettes/` directory.

@@

- the manuscript as submitted (in MS Word format) and its Rmd source file (in the `paper/` directory)  
- supplementary information source files (in R markdown format) and executed versions  
- all the figures that are included in the paper (in the `figures/` directory)

@@

This repository is organized as an R package. There are no actual R functions in this package - all the R code is in the Rmd file. I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.

@@

```{r eval=FALSE}
git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
```

@@

The package has a number of dependencies on other R packages, and programs outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simpify access to the compendium. First is the `packrat/` directory, which contains the source code for all the packages we depend on. If all works well, these will be installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio. <!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/Reproducible.Plant.Pathology?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/Reproducible.Plant.Pathology)
[![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/phytopathology/Reproducible.Plant.Pathology are the development versions and may have changed since the report was published.

@@

Adam H Sparks (adamhsparks@gmail.com)  
Emerson M Del Ponte (delponte@ufv.br)  
Zachary Foster (zacharyfoster1989@gmail.com)  
Niklaus J Grünwald (grunwaln@science.oregonstate.edu)

@@

This repository is our research compendium that details our methodology for examining the state of reproducible research in plant pathology. The compendium contains all data, code, and text associated with the publication XXXX published in XXX. The `R markdown format` (`Rmd`) files in the `inst/paper/` directory contain details of how all the analyses reported in the paper were conducted. Detailed instructions on methods used and how to rerun the analysis to reproduce the results are found in the vignettes, in the `vingettes/` directory.

@@

- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in the `paper/` directory)  
- supplementary information source files (in `Rmd` format) and executed versions  
- all the figures that are included in the paper (in the `figures/` directory)

@@

This repository is organized as an R package. There is one R function, `doi2bib()`, that is used in this repository, along with the data, `assigned_article_notes.rda` that are located in `data` directory. We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.

@@

```
git clone https://github.com/phytopathology/Reproducible.Plant.Pathology.git
```

@@

The package has a number of dependencies on other R packages, and programs outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the source code for all the packages we depend on. If all works well, these will be installed on your computer when you open `Reproducible.Plant.Pathology.Rproj` in RStudio. <!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.

### 2017-04-23 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Finalise conversion to R package
Ready for articles to be evaluated by us

Need to add bib entries to bib file in `inst/paper`

_Other changes_

- Add coverage
- Check spelling
- Finalise fetching references
- Add “examined_articles.bib” to `inst/paper`
- New function to get bib entries given a doi, `doi2bib()`
- Clean up vignettes
- Clean up README
- Use Travis and Appveyor
- Update packrat repository

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3. Zachary S. L. Foster: Department of Botany and Plant Pathology, ORegon State Unviersity, Corvallis, OR 97330, USA
4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA

@@

# MAIN TEXT
Reproductibility and replicability in scientific research have once again been
highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.

@@

## BEST METHODS FOR REPRODUCIBLE RESEARCH
* Provide definitions (provide defintions for terms used so it's clear)
* Data
  * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
* When publishing
  * Provide data
  * Provide code
* Using GitHub for code (and small data?)
* Using Figshare or Zenodo vs a lab website (DOIs, other reasons)

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Example from my lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material

## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
The top 20 plant pathology discipline journals as ranked by Google Scholar, https://scholar.google.com/ (accessed 05 Dec. 2016), were used to create a database of journals from which to randomly select articles for inspection. One hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected start pages assigned to a randomised list of the 20 journals [@Sparks2017]. The start pages list was numbered from page one and went to 150. This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value. This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.

The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2016].

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3. Zachary S. L. Foster: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR 97330, USA
4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA

@@

# MAIN TEXT
Reproducibility and replicability in scientific research have once again been
highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.

@@

## BEST METHODS FOR REPRODUCIBLE RESEARCH
* Provide definitions (provide definitions for terms used so it's clear)
* Data
  * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
* When publishing
  * Provide data
  * Provide code
* Using GitHub for code (and small data?)
* Using Figshare or Zenodo vs a lab website (DOIs, other reasons)

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with reproducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explain in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean tied.
* Example from Grünwald lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material

## RANDOM SAMPLING OF ARTICLES FROM THE TOP 20 PLANT PATHOLOGY JOURNALS
The 21 plant pathology discipline journals were selected by the authors as representations of discipline-based journals where others in the field of phytopathology are likely to publish were used to create a database of journals from which to randomly select articles for inspection. Two hundred articles were randomly selected from 2012 to 2016 from a list of randomly selected pages assigned to a randomised list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal. In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found. Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository. The pages list was numbered from page one and went to 150. This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value. This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.

The list of journals was saved as a comma separated value (CSV) file and imported into R [@R2017].
